Milk intake and risk of mortality risk in the Japan Collaborative Cohort Study - a Bayesian survival analysis

### 2020-07-07 Paperfolder/Paperfolder.Rmd
updated tables and results finished

---
title: Milk intake and risk of mortality risk in the Japan Collaborative Cohort Study - a Bayesian survival analysis 
author:
  - name: Chaochen Wang
    affil: 1,*
    orcid: 0000-0001-5533-1497
  - name: Hiroshi Yatsuya
    affil: 2 
    orcid: 0000-0002-6220-9251
  - name: Yingsong Lin
    affil: 1
    orcid: 0000-0003-0214-3649
  - name: Tae Sasakabe 
    affil: 1 
    orcid: 0000-0002-7417-5693
  - name: Sayo Kawai
    affil: 1
    orcid: 0000-0002-5156-4880
  - name: Shogo Kikuchi
    affil: 1
    orcid: 0000-0001-9499-9668
  - name: Hiroyasu Iso
    affil: 3
    orcid: 0000-0002-9241-7289 
  - name: Akiko Tamakoshi
    affil: 4
    orcid: 0000-0002-9761-3879 
affiliation:
  - num: 1
    address: |
      Department of Public Health, Aichi Medical University School of Medicine, Nagakute, Japan
#    email: chaochen@wangcc.me
  - num: 2
    address: |
      Departmet of Public Health, Fujita Health University School of Medicine, Toyoake, Japan
  - num: 3
    address: |
      Public Health, Department of Social Medicine, Osaka University Graduate School of Medicine, Osaka, Japan
  - num: 4
    address: |
      Department of Public Health, Faculty of Medicine, Hokkaido University, Sapporo, Japan
#    email: yatsuya@gmail.com
# firstnote to eighthnote
# firstnote: |
#   Current address: Updated affiliation
# secondnote: |
#   These authors contributed equally to this work.
correspondence: |
  Email.: chaochen@wangcc.me; Tel.: +81-561-62-3311. Department of Public Health, Aichi Medical University School of Medicine, 1-1 Yazakokarimata, Nagakute, Aichi, 480-1195, Japan (C.W.)
journal: nutrients
type: article
status: submit
bibliography: milk.bib
# appendix: appendix.tex
# simplesummary: |
#  A Simple summary goes here.
abstract: |
  A single paragraph of about 200 words maximum. For research articles, 
  abstracts should give a pertinent overview of the work. We strongly encourage
  authors to use the following style of structured abstracts, but without 
  headings: 1) Background: Place the question addressed in a broad context and
  highlight the purpose of the study; 2) Methods: Describe briefly the main
  methods or treatments applied; 3) Results: Summarize the article's main 
  findings; and 4) Conclusion: Indicate the main conclusions or interpretations. 
  The abstract should be an objective representation of the article, it must not 
  contain results which are not presented and substantiated in the main text and 
  should not exaggerate the main conclusions.
keywords: |
  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
  to the article, yet reasonably common within the subject discipline.).
acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly 
  indicate grants that you have received in support of your research work. 
  Clearly state if you received funds for covering the costs to publish in open 
  access.
authorcontributions: |
  ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.''
conflictsofinterest: |
  The authors declare no conflict of interest. The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, an in the decision to publish the results.
# sampleavailability: |
#   Samples of the compounds ...... are available from the authors.
abbreviations:
  - short: JACC
    long: Japan Collaborative Cohort 
  - short: FFQ
    long: Food Frequency Questionnaire
  - short: MCMC
    long: Markov Chain Monte Carlo
  - short: JAGS
    long: Just Another Gibbs Samplers
output: rticles::mdpi_article
---

@@

The total follow-up was 1555073 person-years (median = 19.3 years), during which 2675 death from stroke was confirmed (1352 men and 1323 women). Among these stroke mortality, 957 were cerebral infarction (520 men and 437 women), and 952 were hemorrhagic stroke (432 men and 520 women).

As listed in \textbf{Table \ref{tab:tab1f}}, compared with those who chose "never" as their milk intake frequency at the baseline, milk drinkers were less likely to be a current smoker or a daily alcohol consumer in both men and women. Furthermore, people consumed milk more than 1-2 times/month were more likely to be a daily consumers of vegetable, fruit  as well as coffee, and more likely to join exercise more than 1 hour/week among either sex.

Table

@@

<!-- This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn. -->

<!-- ## Subsection Heading Here -->

<!-- Subsection text here. -->

<!-- ### Subsubsection Heading Here -->

<!-- Bulleted lists look like this: -->

<!-- * First bullet -->
<!-- * Second bullet -->
<!-- * Third bullet -->

<!-- Numbered lists can be added as follows: -->

<!-- 1. First item -->
<!-- 2. Second item -->
<!-- 3. Third item -->

<!-- The text continues here. -->

<!-- All figures and tables should be cited in the main text as Figure 1, Table 1, etc. -->

<!-- \begin{figure}[H] -->
<!-- \centering -->
<!-- \includegraphics[width=3 cm]{logo-mdpi} -->
<!-- \caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.} -->
<!-- \end{figure} -->

@@

kable(dt, format = "latex", caption = "Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in men.", booktabs = T, linesep = "") %>%
    # collapse_rows(columns = 1, valign = "top") %>% 
  pack_rows("Model 0", 4, 7) %>%
  pack_rows("Model 1", 8, 11) %>%
  pack_rows("Model 2", 12, 15) %>%
kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
  # add_header_above(c(" ", "Estimated HR in Men" = 4, "Estimated HR in Women" = 4)) %>% 
  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", "Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1."))

```

<!-- \begin{table}[H] -->
<!-- \caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.} -->
<!-- \centering -->
<!-- %% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used. -->
<!-- \begin{tabular}{ccc} -->
<!-- \toprule -->
<!-- \textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\ -->
<!-- \midrule -->
<!-- entry 1		& data			& data\\ -->
<!-- entry 2		& data			& data\\ -->
<!-- \bottomrule -->
<!-- \end{tabular} -->
<!-- \end{table} -->

<!-- This is an example of an equation: -->

<!-- \begin{equation} -->
<!-- \mathbb{S} -->
<!-- \end{equation} -->
<!-- If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph. -->

<!-- Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows: -->
<!-- Example of a theorem: -->
<!-- \begin{Theorem} -->
<!-- Example text of a theorem. -->
<!-- \end{Theorem} -->

<!-- The text continues here. Proofs must be formatted as follows: -->

<!-- Example of a proof: -->
<!-- \begin{proof}[Proof of Theorem 1] -->
<!-- Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to. -->
<!-- \end{proof} -->
<!-- The text continues here. -->

<!-- Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted. -->

<!-- This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex. -->

<!-- # Patents -->

<!-- This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript. -->

>>>>

---
title: Milk intake and risk of mortality risk in the Japan Collaborative Cohort Study - a Bayesian survival analysis 
author:
  - name: Chaochen Wang
    affil: 1,*
    orcid: 0000-0001-5533-1497
  - name: Hiroshi Yatsuya
    affil: 2 
    orcid: 0000-0002-6220-9251
  - name: Yingsong Lin
    affil: 1
    orcid: 0000-0003-0214-3649
  - name: Tae Sasakabe 
    affil: 1 
    orcid: 0000-0002-7417-5693
  - name: Sayo Kawai
    affil: 1
    orcid: 0000-0002-5156-4880
  - name: Shogo Kikuchi
    affil: 1
    orcid: 0000-0001-9499-9668
  - name: Hiroyasu Iso
    affil: 3
    orcid: 0000-0002-9241-7289 
  - name: Akiko Tamakoshi
    affil: 4
    orcid: 0000-0002-9761-3879 
affiliation:
  - num: 1
    address: |
      Department of Public Health, Aichi Medical University School of Medicine, Nagakute, Japan
#    email: chaochen@wangcc.me
  - num: 2
    address: |
      Departmet of Public Health, Fujita Health University School of Medicine, Toyoake, Japan
  - num: 3
    address: |
      Public Health, Department of Social Medicine, Osaka University Graduate School of Medicine, Osaka, Japan
  - num: 4
    address: |
      Department of Public Health, Faculty of Medicine, Hokkaido University, Sapporo, Japan
#    email: yatsuya@gmail.com
# firstnote to eighthnote
# firstnote: |
#   Current address: Updated affiliation
# secondnote: |
#   These authors contributed equally to this work.
correspondence: |
  Email.: chaochen@wangcc.me; Tel.: +81-561-62-3311. Department of Public Health, Aichi Medical University School of Medicine, 1-1 Yazakokarimata, Nagakute, Aichi, 480-1195, Japan (C.W.)
journal: nutrients
type: article
status: submit
bibliography: milk.bib
# appendix: appendix.tex
# simplesummary: |
#  A Simple summary goes here.
abstract: |
  A single paragraph of about 200 words maximum. For research articles, 
  abstracts should give a pertinent overview of the work. We strongly encourage
  authors to use the following style of structured abstracts, but without 
  headings: 1) Background: Place the question addressed in a broad context and
  highlight the purpose of the study; 2) Methods: Describe briefly the main
  methods or treatments applied; 3) Results: Summarize the article's main 
  findings; and 4) Conclusion: Indicate the main conclusions or interpretations. 
  The abstract should be an objective representation of the article, it must not 
  contain results which are not presented and substantiated in the main text and 
  should not exaggerate the main conclusions.
keywords: |
  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
  to the article, yet reasonably common within the subject discipline.).
acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly 
  indicate grants that you have received in support of your research work. 
  Clearly state if you received funds for covering the costs to publish in open 
  access.
authorcontributions: |
  ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.''
conflictsofinterest: |
  The authors declare no conflict of interest. The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, an in the decision to publish the results.
# sampleavailability: |
#   Samples of the compounds ...... are available from the authors.
abbreviations:
  - short: JACC
    long: Japan Collaborative Cohort 
  - short: FFQ
    long: Food Frequency Questionnaire
  - short: MCMC
    long: Markov Chain Monte Carlo
  - short: JAGS
    long: Just Another Gibbs Samplers
  - short: HR
    long: hazard ratio
  - short: sd
    long: standard deviation
  - short: CrI
    long: credible interval
output: rticles::mdpi_article
---

@@

The total follow-up was 1555073 person-years (median = 19.3 years), during which 2675 death from stroke was confirmed (1352 men and 1323 women). Among these stroke mortality, 952 were hemorrhagic stroke (432 men and 520 women), and 957 were cerebral infarction (520 men and 437 women).

@@

As listed in \textbf{Table \ref{tab:tab1f}}, compared with those who chose "never" as their milk intake frequency at baseline, milk drinkers were less likely to be a current smoker or a daily alcohol consumer in both men and women. Furthermore, people consumed milk more than 1-2 times/month were more likely to be a daily consumers of vegetable, fruit  as well as coffee, and more likely to join exercise more than 1 hour/week among either sex.

Detailed results from the Bayesian survival models (crude, age-adjusted and multivariable adjusted) according to the frequency of milk intake separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and \textbf{Table \ref{tab:tab3}} (women). Compared to those who never had milk, both men and women had lower hazard of dying from total stroke in crude models. Chances that the posterior HRs were estimated to be lower than 1 for those who had at least 1-2 times/month was higher than 86.5% in men and more than 94.6% in women. However, lower hazard was observed to remain after age or multivariable adjustment only in men. Specifically, the mean (sd; 95% CrI) of posterior multivariable-adjusted HRs for daily male consumers of milk was 0.80 (sd = 0.07; 95% CrI: 0.69, 0.93) with a probability of 99.0% to be smaller than the null value (=1). Daily female milk consumers had posterior HRs that was distributed with mean (sd) of 0.95 (sd = 0.12; 95% CrI: 0.80, 1.17) which had 78.0% of chance that their HRs could be lower than 1.

Posterior distributions of HRs for mortality from hemorrhagic stroke were found to contain the null value for either men or women among all fitted models. In contrast, men who had milk intake frequency higher than 1-2 times/week were found to be associated with averagely 26%-37% lower hazard of dying from cerebral infarction compared with men who never drank milk (Model 2 in \textbf{Table \ref{tab:tab2}}). We were more than 95.7% sure that these posterior HRs could be lower than 1. No associations were observed between milk intake and hazard of cerebral infarction among women.

In the JACC study cohort, we observed that

@@

kable(dt, format = "latex", caption = "Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in men (JACC study, 1988-2009).", booktabs = T, linesep = "", align = "lccccc") %>%
    # collapse_rows(columns = 1, valign = "top") %>% 
  pack_rows("Model 0", 4, 7) %>%
  pack_rows("Model 1", 8, 11) %>%
  pack_rows("Model 2", 12, 15) %>%
    row_spec(15,  hline_after = TRUE) %>%
    pack_rows("Model 0", 17, 20) %>%
  pack_rows("Model 1", 21, 24) %>%
  pack_rows("Model 2", 25, 28) %>%
      row_spec(28,  hline_after = TRUE) %>%
  pack_rows("Model 0", 30, 33) %>%
  pack_rows("Model 1", 34, 37) %>%
  pack_rows("Model 2", 38, 41) %>%
kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
  # add_header_above(c(" ", "Estimated HR in Men" = 4, "Estimated HR in Women" = 4)) %>% 
  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", " Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.", "Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model.", "Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of",  "hypertension, diabetes, kidney/liver diseases, exercise, sleep duration, coffee intake, education level.")) 
```

```{r tab3, echo=FALSE, eval=TRUE, message=FALSE}
dt <- read.csv("tab/HRAFTweibF.csv", header = T)
# dt <- data.frame(`Stroke` = c(rep("Total stroke", 15)), dt)
names(dt) <- c(" ", "Never", "1-2 times/Month", "1-2 times/Week", "3-4 times/Week", "Almost Daily")

kable(dt, format = "latex", caption = "Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in women (JACC study, 1988-2009).", booktabs = T, linesep = "", align = "lccccc") %>%
    # collapse_rows(columns = 1, valign = "top") %>% 
  pack_rows("Model 0", 4, 7) %>%
  pack_rows("Model 1", 8, 11) %>%
  pack_rows("Model 2", 12, 15) %>%
  row_spec(15,  hline_after = TRUE) %>%
  pack_rows("Model 0", 17, 20) %>%
  pack_rows("Model 1", 21, 24) %>%
  pack_rows("Model 2", 25, 28) %>%
  row_spec(28,  hline_after = TRUE) %>%
  pack_rows("Model 0", 30, 33) %>%
  pack_rows("Model 1", 34, 37) %>%
  pack_rows("Model 2", 38, 41) %>%
kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
  # add_header_above(c(" ", "Estimated HR in Men" = 4, "Estimated HR in Women" = 4)) %>% 
  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", " Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.", "Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model.", "Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of",  "hypertension, diabetes, kidney/liver diseases, exercise, sleep duration, coffee intake, education level.")) 
```

### 2020-07-07 Paperfolder/Paperfolder.tex
updated tables done
updated table 2 men 50%
updted table 2
updated table 2 80% and table 3 50%
updated tables and results finished

The total follow-up was 1555073 person-years (median = 19.3 years),
during which 2675 death from stroke was confirmed (1352 men and 1323
women). Among these stroke mortality, 957 were cerebral infarction (520
men and 437 women), and 952 were hemorrhagic stroke (432 men and 520
women).

As listed in \textbf{Table \ref{tab:tab1f}}, compared with those who
chose ``never'' as their milk intake frequency at the baseline, milk
drinkers were less likely to be a current smoker or a daily alcohol
consumer in both men and women. Furthermore, people consumed milk more
than 1-2 times/month were more likely to be a daily consumers of
vegetable, fruit as well as coffee, and more likely to join exercise
more than 1 hour/week among either sex.

Table

@@

@@

\begin{tabular}[t]{llllll}

@@

\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 86.50\% & 99.90\% & 99.70\% & 93.47\%\\

@@

\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 58.70\% & 97.31\% & 96.05\% & 100.00\%\\

@@

\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 50.61\% & 93.73\% & 89.62\% & 99.04\%\\

@@

\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 1.01 (0.08) &  &  & \\
\hspace{1em}95\% CrI &  & (0.75, 1.04) &  &  & \\
\rowcolor{gray!6}  \hspace{1em}MCSE &  &  &  &  \vphantom{5} & \\
\hspace{1em}Pr(HR < 1) &  &  &  &  \vphantom{5} & \\

@@

\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 &  &  &  \vphantom{4} & \\
\hspace{1em}95\% CrI &  &  &  &  \vphantom{4} & \\
\rowcolor{gray!6}  \hspace{1em}MCSE &  &  &  &  \vphantom{4} & \\
\hspace{1em}Pr(HR < 1) &  &  &  &  \vphantom{4} & \\

@@

\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 &  &  &  \vphantom{3} & \\
\hspace{1em}95\% CrI &  &  &  &  \vphantom{3} & \\
\rowcolor{gray!6}  \hspace{1em}MCSE &  &  &  &  \vphantom{3} & \\
\hspace{1em}Pr(HR < 1) &  &  &  &  \vphantom{3} & \\

@@

\hspace{1em}MeanHR (SD) & 1 &  &  &  \vphantom{2} & \\
\rowcolor{gray!6}  \hspace{1em}95\% CrI &  &  &  &  \vphantom{2} & \\
\hspace{1em}MCSE &  &  &  &  \vphantom{2} & \\
\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) &  &  &  &  \vphantom{2} & \\

@@

\hspace{1em}MeanHR (SD) & 1 &  &  &  \vphantom{1} & \\
\rowcolor{gray!6}  \hspace{1em}95\% CrI &  &  &  &  \vphantom{1} & \\
\hspace{1em}MCSE &  &  &  &  \vphantom{1} & \\
\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) &  &  &  &  \vphantom{1} & \\

@@

\hspace{1em}MeanHR (SD) & 1 &  &  &  & \\
\rowcolor{gray!6}  \hspace{1em}95\% CrI &  &  &  &  & \\
\hspace{1em}MCSE &  &  &  &  & \\
\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) &  &  &  &  & \\

@@

@@

\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 &  &  &  \vphantom{5} & \\
\hspace{1em}95\% CrI & - &  &  &  \vphantom{5} & \\
\rowcolor{gray!6}  \hspace{1em}MCSE & - &  &  &  \vphantom{5} & \\
\hspace{1em}Pr(HR < 1) & - &  &  &  \vphantom{5} & \\

@@

\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 &  &  &  \vphantom{4} & \\
\hspace{1em}95\% CrI & - &  &  &  \vphantom{4} & \\
\rowcolor{gray!6}  \hspace{1em}MCSE & - &  &  &  \vphantom{4} & \\
\hspace{1em}Pr(HR < 1) & - &  &  &  \vphantom{4} & \\

@@

\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 &  &  &  \vphantom{3} & \\
\hspace{1em}95\% CrI & - &  &  &  \vphantom{3} & \\
\rowcolor{gray!6}  \hspace{1em}MCSE & - &  &  &  \vphantom{3} & \\
\hspace{1em}Pr(HR < 1) & - &  &  &  \vphantom{3} & \\

@@

\hspace{1em}MeanHR (SD) & 1 &  &  &  \vphantom{2} & \\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - &  &  &  \vphantom{2} & \\
\hspace{1em}MCSE & - &  &  &  \vphantom{2} & \\
\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - &  &  &  \vphantom{2} & \\

@@

\hspace{1em}MeanHR (SD) & 1 &  &  &  \vphantom{1} & \\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - &  &  &  \vphantom{1} & \\
\hspace{1em}MCSE & - &  &  &  \vphantom{1} & \\
\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - &  &  &  \vphantom{1} & \\

@@

\hspace{1em}MeanHR (SD) & 1 &  &  &  & \\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - &  &  &  & \\
\hspace{1em}MCSE & - &  &  &  & \\
\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - &  &  &  & \\

@@

\noindent
\begin{tabular}{@{}ll}
JACC & Japan Collaborative Cohort \\
FFQ & Food Frequency Questionnaire \\
MCMC & Markov Chain Monte Carlo \\
JAGS & Just Another Gibbs Samplers \\
\end{tabular}}

>>>>

The total follow-up was 1555073 person-years (median = 19.3 years),
during which 2675 death from stroke was confirmed (1352 men and 1323
women). Among these stroke mortality, 952 were hemorrhagic stroke (432
men and 520 women), and 957 were cerebral infarction (520 men and 437
women).

@@

As listed in \textbf{Table \ref{tab:tab1f}}, compared with those who
chose ``never'' as their milk intake frequency at baseline, milk
drinkers were less likely to be a current smoker or a daily alcohol
consumer in both men and women. Furthermore, people consumed milk more
than 1-2 times/month were more likely to be a daily consumers of
vegetable, fruit as well as coffee, and more likely to join exercise
more than 1 hour/week among either sex.

Detailed results from the Bayesian survival models (crude, age-adjusted
and multivariable adjusted) according to the frequency of milk intake
separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and
\textbf{Table \ref{tab:tab3}} (women). Compared to those who never had
milk, both men and women had lower hazard of dying from total stroke in
crude models. Chances that the posterior HRs were estimated to be lower
than 1 for those who had at least 1-2 times/month was higher than 86.5\%
in men and more than 94.6\% in women. However, lower hazard was observed
to remain after age or multivariable adjustment only in men.
Specifically, the mean (sd; 95\% CrI) of posterior
multivariable-adjusted HRs for daily male consumers of milk was 0.80 (sd
= 0.07; 95\% CrI: 0.69, 0.93) with a probability of 99.0\% to be smaller
than the null value (=1). Daily female milk consumers had posterior HRs
that was distributed with mean (sd) of 0.95 (sd = 0.12; 95\% CrI: 0.80,
1.17) which had 78.0\% of chance that their HRs could be lower than 1.

Posterior distributions of HRs for mortality from hemorrhagic stroke
were found to contain the null value for either men or women among all
fitted models. In contrast, men who had milk intake frequency higher
than 1-2 times/week were found to be associated with averagely 26\%-37\%
lower hazard of dying from cerebral infarction compared with men who
never drank milk (Model 2 in \textbf{Table \ref{tab:tab2}}). We were
more than 95.7\% sure that these posterior HRs could be lower than 1. No
associations were observed between milk intake and hazard of cerebral
infarction among women.

In the JACC study cohort, we observed that

@@

\begin{tabular}[t]{lccccc}

@@

\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 86.5\% & 99.9\% & 99.7\% & 93.5\%\\

@@

\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 58.7\% & 97.3\% & 96.1\% & 100.0\%\\

@@

\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 50.6\% & 93.7\% & 89.6\% & 99.0\%\\
\hline

@@

\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 1.03 (0.19) & 0.82 (0.14) & 0.84 (0.15) & 0.97 (0.13)\\
\hspace{1em}95\% CrI & - & (0.70, 1.46) & (0.56, 1.14) & (0.60, 1.17) & (0.75, 1.26)\\
\rowcolor{gray!6}  \hspace{1em}MCSE & - & 0.0066 & 0.0057 & 0.0057 & 0.0062\\
\hspace{1em}Pr(HR < 1) & - & 47.2\% & 88.4\% & 86.3\% & 63.1\%\\

@@

\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 1.11 (0.21) & 0.88 (0.16) & 0.90 (0.16) & 0.88 (0.12)\\
\hspace{1em}95\% CrI & - & (0.75, 1.58) & (0.63, 1.25) & (0.63, 1.24) & (0.67, 1.14)\\
\rowcolor{gray!6}  \hspace{1em}MCSE & - & 0.0091 & 0.0067 & 0.0073 & 0.0076\\
\hspace{1em}Pr(HR < 1) & - & 31.6\% & 79.7\% & 76.6\% & 87.6\%\\

@@

\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 1.14 (0.22) & 0.92 (0.17) & 0.95 (0.18) & 0.95 (0.14)\\
\hspace{1em}95\% CrI & - & (0.75, 1.61) & (0.63, 1.29) & (0.65, 1.37) & (0.71, 1.27)\\
\rowcolor{gray!6}  \hspace{1em}MCSE & - & 0.0093 & 0.0075 & 0.0098 & 0.0082\\
\hspace{1em}Pr(HR < 1) & - & 28.8\% & 72.4\% & 64.4\% & 69.3\%\\
\hline

@@

\hspace{1em}MeanHR (SD) & 1 & 0.65 (0.12) & 0.59 (0.09) & 0.64 (0.09) & 0.71 (0.09)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.46, 0.92) & (0.43, 0.79) & (0.47, 0.85) & (0.56, 0.89)\\
\hspace{1em}MCSE & - & 0.0042 & 0.0037 & 0.0036 & 0.0038\\
\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 99.1\% & 99.9\% & 99.7\% & 99.5\%\\

@@

\hspace{1em}MeanHR (SD) & 1 & 0.73 (0.13) & 0.65 (0.10) & 0.70 (0.11) & 0.58 (0.07)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.49, 1.02) & (0.48, 0.88) & (0.51, 0.94) & (0.46, 0.72)\\
\hspace{1em}MCSE & - & 0.0045 & 0.0035 & 0.0041 & 0.0029\\
\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 96.9\% & 99.8\% & 98.9\% & 100.0\%\\

@@

\hspace{1em}MeanHR (SD) & 1 & 0.73 (0.14) & 0.67 (0.11) & 0.72 (0.12) & 0.61 (0.08)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.50, 1.04) & (0.48, 0.91) & (0.52, 0.99) & (0.48, 0.79)\\
\hspace{1em}MCSE & - & 0.0049 & 0.0047 & 0.0061 & 0.0052\\
\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 96.1\% & 99.1\% & 97.5\% & 99.8\%\\

@@

\hline

@@

\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 0.73 (0.16) & 0.98 (0.15) & 0.87 (0.14) & 0.89 (0.11)\\
\hspace{1em}95\% CrI & - & (0.47, 1.08) & (0.71, 1.31) & (0.64, 1.16) & (0.71, 1.15)\\
\rowcolor{gray!6}  \hspace{1em}MCSE & - & 0.0058 & 0.0071 & 0.0061 & 0.0065\\
\hspace{1em}Pr(HR < 1) & - & 94.7\% & 58.1\% & 83.1\% & 83.0\%\\

@@

\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 0.84 (0.18) & 1.17 (0.18) & 1.06 (0.17) & 0.93 (0.12)\\
\hspace{1em}95\% CrI & - & (0.54, 1.24) & (0.86, 1.58) & (0.76, 1.45) & (0.73, 1.19)\\
\rowcolor{gray!6}  \hspace{1em}MCSE & - & 0.0065 & 0.0089 & 0.0084 & 0.0069\\
\hspace{1em}Pr(HR < 1) & - & 81.6\% & 16.9\% & 38.9\% & 74.6\%\\

@@

\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 0.85 (0.18) & 1.21 (0.18) & 1.13 (0.17) & 1.03 (0.12)\\
\hspace{1em}95\% CrI & - & (0.56, 1.30) & (0.90, 1.62) & (0.84, 1.52) & (0.81, 1.29)\\
\rowcolor{gray!6}  \hspace{1em}MCSE & - & 0.0051 & 0.0067 & 0.0039 & 0.0047\\
\hspace{1em}Pr(HR < 1) & - & 79.6\% & 12.7\% & 33.4\% & 71.4\%\\
\hline

@@

\hspace{1em}MeanHR (SD) & 1 & 1.01 (0.13) & 0.82 (0.14) & 0.59 (0.14) & 0.76 (0.16)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.69, 1.48) & (0.60, 1.13) & (0.43, 0.84) & (0.59, 0.99)\\
\hspace{1em}MCSE & - & 0.0087 & 0.0079 & 0.0064 & 0.0071\\
\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 51.9\% & 75.6\% & 97.6\% & 96.1\%\\

@@

\hspace{1em}MeanHR (SD) & 1 & 1.29 (0.14) & 1.15 (0.13) & 0.86 (0.14) & 0.86 (0.15)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.88, 1.89) & (0.84, 1.58) & (0.61, 1.20) & (0.67, 1.09)\\
\hspace{1em}MCSE & - & 0.0071 & 0.0072 & 0.0095 & 0.0054\\
\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 36.7\% & 42.1\% & 78.7\% & 88.9\%\\

@@

\hspace{1em}MeanHR (SD) & 1 & 1.30 (0.11) & 1.18 (0.09) & 0.87 (0.10) & 0.93 (0.07)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.88, 1.92) & (0.86, 1.63) & (0.62, 1.23) & (0.72, 1.19)\\
\hspace{1em}MCSE & - & 0.0055 & 0.0057 & 0.0067 & 0.0047\\
\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 35.1\% & 39.9\% & 75.6\% & 80.1\%\\

@@

\noindent
\begin{tabular}{@{}ll}
JACC & Japan Collaborative Cohort \\
FFQ & Food Frequency Questionnaire \\
MCMC & Markov Chain Monte Carlo \\
JAGS & Just Another Gibbs Samplers \\
HR & hazard ratio \\
sd & standard deviation \\
CrI & credible interval \\
\end{tabular}}
